\documentclass[11pt]{article}
\usepackage{graphicx} % To include graphics 
\usepackage[tbtags]{amsmath} % tbtags to make eq number at last line
\usepackage{amssymb}
%\usepackage{wrapfig} % For figures next to text
\usepackage{booktabs} % Better tables
% \usepackage{physics} 
\usepackage{cases} % For cases with separate labels
\usepackage{hyperref}% For cross-referencing
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}
%\usepackage{pgfplots} % For drawing graphs
\usepackage{parskip} % To remove indentation and set paragraph spacing
\usepackage[margin=1in]{geometry}
%\usepackage{cancel} % To cancel out terms
\usepackage{listings} % To write code
\usepackage{xcolor} % To write color text/math by \textcolor{color}{text}
\usepackage{enumitem} % Better list environment
\usepackage{fancyhdr} % For custom headers and footers
% \usepackage{amsthm} % To write theorems and proofs
% \renewcommand\qedsymbol{$\blacksquare$}
% \usepackage{algorithm}
% \usepackage{algpseudocode}

%%%%%%%%%% Configure fancy headers %%%%%%%%%%
\pagestyle{fancy}

%%%%%%%%%% listings config (for writing code) %%%%%%%%%%
% \definecolor{codegreen}{rgb}{0,0.6,0}
% \definecolor{codegray}{rgb}{0.5,0.5,0.5}
% \definecolor{codepurple}{rgb}{0.58,0,0.82}
% \definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% \lstdefinestyle{mystyle}{
%     frame=tb,
%     basicstyle=\ttfamily,
%     backgroundcolor=\color{backcolour},   
%     % commentstyle=\color{codegreen},
%     % keywordstyle=\color{magenta},
%     % stringstyle=\color{codepurple},
%     breakatwhitespace=false,         
%     breaklines=true,                 
%     captionpos=b,                    
%     keepspaces=true,                 
%     numbers=left,                    
%     numbersep=5pt,                  
%     showspaces=false,                
%     showstringspaces=false,
%     showtabs=false,                  
%     tabsize=4
% }
% \lstset{style=mystyle}

% Title
\title{CSCI3100 Project Requirements Specification}
\author{
    \textbf{Group 17} \\[1em]
    \begin{tabular}{ll}
        Ng Ching Yin & (1155175606) \\
        Lam Hoi Chun & (1155192755) \\
        Lai Wing Fai & () \\
        Zou Zhi Hong & (1155204947)
    \end{tabular}
}
\date{\today}

\begin{document}
\maketitle

% Table of contents
{
    \hypersetup{linkcolor=black}
    \tableofcontents
}

\newpage

% Document Revision History
% Update this only before pull request, don't update every commit
\section{Document Revision History}
\begin{table}[h]
    \centering
    \caption{Document Revision History}
    \begin{tabular}{p{1.5cm} p{6cm} p{2cm} p{3cm}}
        \toprule
        Version & Revised By & Revision Date & Comments \\
        \midrule
        0.0.1 & Ng Ching Yin, Lam Hoi Chun, Zou Zhi Hong & 11 Nov 2025 & Initial release \\
        \bottomrule
    \end{tabular}
    \label{tab:docs_rev_hist}
\end{table}

% Introduction
\section{Introduction}

\subsection{Purpose}

This document defines the user requirements for the new software project management
tool for the Demon Slayers Corps. This document will serve as a basis for both
stakeholders and developers in subsequent development activities.

\subsection{Project Background}

In a realm where demon slayers fought valiantly against the forces of darkness, the boss of
the Demon Slayer Corps struggled with managing their software projects, leading to chaotic
battles and the tragic loss of many brave warriors. Recognizing the dire need for better
organization, Kei, the CSCI3100 lecturer, and his eager students decided to step in, determined
to create a robust software project management tool tailored specifically for the Demon Slayers.

With their combined skills in coding and project management, they envisioned a system that
would streamline communication, track progress, and allocate resources effectively, ultimately
empowering the slayers to focus on their true mission: vanquishing demons and protecting
humanity.

\subsection{Business Objectives}
The high-level business objectives for the project are to:
\begin{enumerate}
    \item reduce inefficiency in task and resource allocation, including
    \begin{itemize}%[leftmargin=*]
        \item[(a)] average time from task creation to assignment;
        \item[(b)] workload variance across team members;
    \end{itemize}
    \item track mission and development progress in real time;
    \item streamline communication among developers;
    \item provide useful tools to facilitate software development;
\end{enumerate}

\subsection{Project Scope}
The new project management tool aims to streamline software team coordination by 
providing task tracking, scheduling, messaging, and an LLM chat interface to accelerate
development workflows.

The major functions to be provided by the tool are listed below:
\begin{enumerate}
    \item Kanban board for task management and progress tracking;
    \item Calendar to track and visualize deadlines;
    \item Discussion system to streamline communication among developers;
    \item LLM chat interface to speed up development progress;
\end{enumerate}

\section{Identified Risks, Assumptions and Constraints}
\subsection{Identified Risks}
\begin{table}[h]
    \centering
    \caption{Identified Risks}
    \begin{tabular}{p{1cm} | p{3.5cm} | p{1.8cm} | p{3cm} | p{1.3cm} | p{2cm}}
        \toprule
        Risk No. 
        & Description 
        & Likelihood 
        & Impact 
        & Rating 
        & Possible Resolutions \\
        
        \midrule
        R1 
        & LLM third-party API failure
        & Medium
        & Slows down \text{development} progress
        & Low 
        & Use \text{multiple} LLM providers; Alert \text{system} to detect \text{failure} \\

        \midrule
        R2
        & LLM abuse; high API cost
        & High
        & Increase API expense significantly
        & High
        & Limit API usage by plan; \\

        \midrule
        R3
        & Local devices / out-of-sync user seeing conflicting information
        & High
        & User confusion and mistrust in the system
        & High
        & Warn user when out-of-sync; \text{Implement} sync \text{recovery} mechanism \\

        \bottomrule
    \end{tabular}
    \label{tab:docs_identified_risks}
\end{table}

\subsection{Assumptions}
\begin{table}[h]
    \centering
    \caption{Assumptions}
    \begin{tabular}{p{2cm} p{3.5cm} p{10cm}}
        \toprule
        Assumption No. 
        & Title 
        & Description \\

        \midrule
        A1
        & Apple minimum OS version 
        & iOS 26, iPadOS 26, and macOS 26  \\

        \bottomrule
    \end{tabular}
    \label{tab:docs_assumptions}
\end{table}

\subsection{Constraints}
\begin{enumerate}
    \item Development Team Expertise: The system shall be developed by
    CSCI3100 students as part of their course project. The design and
    implementation are constrained by the students' current knowledge
    of technologies, databases, and software engineering principles, 
    and must be completed within a single academic semester.
    \item Budgetary Constraints: The project has no monetary budget for
    proprietary software licenses, Application Programming Interface (API)
    calls, or cloud hosting services. The system must be built exclusively
    with free and open-source technologies and frameworks.
    \item LLM Integration Limitation: The integration of the Large Language
    Model (LLM) chat interface is dependent on the availability and usage
    limits of a free-tier or publicly accessible LLM API (e.g., OpenAI GPT,
    Llama). The system cannot guarantee unlimited or high-volume usage without
    incurring costs.
    \item Scope Creep Control: To ensure timely delivery for the semester's end,
    the project scope is fixed upon the agreement of the initial requirements.
    Any proposed additional features will be deferred to a hypothetical "Phase 2" and will
    not be considered for the initial release.
\end{enumerate}

\section{Functional Requirements}
\label{sec:functional_requirements}

\begin{enumerate}
    \item \textbf{User Accounts and Authentication}
    \begin{enumerate}[label=\textbf{FR1-\arabic*.}, leftmargin=2cm]
        \item The system shall allow users to register, sign in, and sign out using email and password.
        \item The system shall support password reset via email.
        \item The system shall support basic roles: Admin and Member.
        \item The system should support common sign in methods (e.g. Google sign in).
    \end{enumerate}

    \item \textbf{Workspaces and Teams}
    \begin{enumerate}[label=\textbf{FR2-\arabic*.}, leftmargin=2cm]
        \item The system shall provide Workspaces (organization/team scope).
        \item Admins shall be able to invite/remove members and assign roles per Workspace.
    \end{enumerate}

    \item \textbf{Kanban Board and Task Management}
    \begin{enumerate}[label=\textbf{FR3-\arabic*.}, leftmargin=2cm]
        \item The system shall provide a Kanban board with drag-and-drop functionality.
        \item Users shall be able to create, read, update, and delete tasks.
        \item Tasks shall support fields: title, description, status, difficulty, tags, deadlines.
    \end{enumerate}

    \item \textbf{Discussion and Collaboration}
    \begin{enumerate}[label=\textbf{FR4-\arabic*.}, leftmargin=2cm]
        \item Each task shall have a comment thread supporting @mentions and attachments.
        \item The system shall support Markdown formatting for comments (headings, lists, code blocks).
    \end{enumerate}

    \item \textbf{Real-time Updates and Collaboration}
    \begin{enumerate}[label=\textbf{FR5-\arabic*.}, leftmargin=2cm]
        \item Board and task updates made by one user shall appear for other online users in near real-time.
        \item The system shall display an out-of-sync warning if a client falls behind and provide a manual refresh action.
    \end{enumerate}

    \item \textbf{Calendar and Scheduling}
    \begin{enumerate}[label=\textbf{FR6-\arabic*.}, leftmargin=2cm]
        \item The system shall provide monthly calendar views of task deadlines.
    \end{enumerate}

    \item \textbf{LLM Chat Interface}
    \begin{enumerate}[label=\textbf{FR7-\arabic*.}, leftmargin=2cm]
        \item The system shall provide a personal LLM chat interface.
        \item The system shall rate-limit LLM requests per user and per workspace to control costs.
        \item The system shall support configuring multiple LLM providers and failover when one provider is unavailable.
        \item The system shall store chat history per project and allow exporting a conversation.
    \end{enumerate}

    \item \textbf{Offline Tolerance and Sync Recovery}
    \begin{enumerate}[label=\textbf{FR8-\arabic*.}, leftmargin=2cm]
        \item The system shall allow reading recently viewed boards/tasks when offline.
        \item Edits made offline shall be queued and synced when connectivity is restored.
    \end{enumerate}

    \item \textbf{Administration}
    \begin{enumerate}[label=\textbf{FR9-\arabic*.}, leftmargin=2cm]
        \item Admins shall be able to configure workspace settings, LLM provider keys, LLM quotas, and feature flags.
        \item Admins shall be able to deactivate users and transfer project ownership.
    \end{enumerate}
\end{enumerate}


\section{Non-Functional Requirements}
\label{sec:non_functional_requirements}

\begin{enumerate}
    \item \textbf{Performance}
    \begin{enumerate}[label=\textbf{NFR1-\arabic*.}, leftmargin=2cm]
        \item Initial application load shall be under 2.5 seconds on a mid-range laptop/phone.
        \item 95\% of API requests shall complete within 500 ms under normal load; 99\% within 1 s.
        \item Real-time updates shall propagate to connected clients within 2 seconds.
    \end{enumerate}

    \item \textbf{Availability}
    \begin{enumerate}[label=\textbf{NFR2-\arabic*.}, leftmargin=2cm]
        \item The system should achieve 99\% monthly uptime.
        \item Planned maintenance windows shall be announced in advance and limited to 2 hours/week.
    \end{enumerate}

    \item \textbf{Reliability and Data Integrity}
    \begin{enumerate}[label=\textbf{NFR3-\arabic*.}, leftmargin=2cm]
        \item Create/update/delete operations shall be atomic and durable.
        \item The system shall prevent or resolve conflicting edits.
    \end{enumerate}

    \item \textbf{Scalability}
    \begin{enumerate}[label=\textbf{NFR4-\arabic*.}, leftmargin=2cm]
        \item The system should support at least 50 concurrent active users per workspace without violating performance targets.
        \item The system should support up to 20,000 tasks per project.
    \end{enumerate}

    \item \textbf{Privacy and LLM Data Handling}
    \begin{enumerate}[label=\textbf{NFR5-\arabic*.}, leftmargin=2cm]
        \item The system shall minimize personal data collection to what is strictly necessary.
        \item The system shall not send secrets or access tokens to LLM providers; task content sent to LLMs shall be user-initiated.
    \end{enumerate}

    \item \textbf{Usability}
    \begin{enumerate}[label=\textbf{NFR6-\arabic*.}, leftmargin=2cm]
        \item New users shall be able to create a project, a board, and a task within 5 minutes without training.
        \item Common operations (create task, assign, move columns) shall require no more than 3 clicks from the board view.
        \item Provide keyboard shortcuts for frequent actions (e.g., create task, quick search).
    \end{enumerate}

    \item \textbf{Compatibility and Cross-Platform Support}
    \begin{enumerate}[label=\textbf{NFR7-\arabic*.}, leftmargin=2cm]
        \item The application shall be available on all major platforms, including Windows, Linux, macOS, iOS, Android and iPadOS.
        \item The UI shall be responsive for desktop, tablet, and mobile breakpoints.
    \end{enumerate}

    \item \textbf{Observability and Alerting}
    \begin{enumerate}[label=\textbf{NFR8-\arabic*.}, leftmargin=2cm]
        \item Basic metrics (request rates, error rates, latency) shall be collected and viewable by developers.
        \item Alerts shall trigger on sustained LLM provider failures, error spikes, and elevated latency.
    \end{enumerate}

    \item \textbf{Deployment and Portability}
    \begin{enumerate}[label=\textbf{NFR9-\arabic*.}, leftmargin=2cm]
        \item The system should provide a containerized deployment.
        \item A developer environment shall be bootstrapped in under 15 minutes with documented steps.
    \end{enumerate}

    \item \textbf{Internationalization and Time Zones}
    \begin{enumerate}[label=\textbf{NFR10-\arabic*.}, leftmargin=2cm]
        \item All dates/times shall be stored in UTC and displayed in the user's local time zone.
        \item The UI shall support localization.
    \end{enumerate}

    \item \textbf{Data Retention and Deletion}
    \begin{enumerate}[label=\textbf{NFR11-\arabic*.}, leftmargin=2cm]
        \item Users must be able to request deletion of their personal data; requests should be fulfilled within 7 days. 
    \end{enumerate}
\end{enumerate}


% \appendix
% \addcontentsline{toc}{section}{Appendix}
% \section*{Appendix}
% \section{References}

\end{document}
