\section{Identified Risks, Assumptions and Constraints}
\subsection{Identified Risks}
\begin{table}[h]
    \centering
    \caption{Identified Risks}
    \begin{tabular}{p{1cm} | p{3.5cm} | p{1.8cm} | p{3cm} | p{1.3cm} | p{3cm}}
        \toprule
        Risk No. 
        & Description 
        & Likelihood 
        & Impact 
        & Rating 
        & Possible Resolutions \\
        
        \midrule
        R1 
        & LLM third-party API failure
        & Medium
        & Slows down development progress
        & Low 
        & Use multiple LLM providers \\

        \midrule
        R2
        & LLM abuse; high API cost
        & High
        & Increase expense significantly
        & High
        & Limit API usage by plan; Provide local LLM with unlimited usage\\

        \midrule
        R3
        & Local devices or out-of-sync user seeing conflicting information
        & High
        & User confusion and mistrust in the system
        & High
        & Implement sync recovery mechanism \\

        \bottomrule
    \end{tabular}
    \label{tab:docs_identified_risks}
\end{table}

\subsection{Assumptions}
\begin{table}[h]
    \centering
    \caption{Assumptions}
    \begin{tabular}{p{2cm} p{3.5cm} p{10cm}}
        \toprule
        Assumption No. 
        & Title 
        & Description \\

        \midrule
        A1
        & Apple minimum OS version 
        & iOS 26, iPadOS 26, and macOS 26  \\

        \midrule
        A2
        & Internet connectivity
        & User should have reliable internet access for collaboration \\

        \bottomrule
    \end{tabular}
    \label{tab:docs_assumptions}
\end{table}

\subsection{Constraints}
\begin{enumerate}
    \item Development Team Expertise: The system shall be developed by
    CSCI3100 students as part of their course project. The design and
    implementation are constrained by the students' current knowledge
    of technologies, databases, and software engineering principles, 
    and must be completed within a single academic semester.
    \item Budget Constraints: The project has no monetary budget for
    proprietary software licenses, API
    calls, or cloud hosting services. The system must be built exclusively
    with free or open-source technologies and frameworks.
    \item LLM Integration Limitation: The integration of the Large Language
    Model (LLM) chat interface is dependent on the availability and usage
    limits of a free-tier or publicly accessible LLM API (e.g., OpenAI GPT,
    Llama). The system cannot guarantee unlimited or high-volume usage without
    incurring costs.
    \item Scope Creep Control: To ensure timely delivery for the semester's end,
    the project scope is fixed upon the agreement of the initial requirements.
    Any proposed additional features will be deferred to a hypothetical "Phase 2" and will
    not be considered for the initial release.
\end{enumerate}