\section{Introduction}

\subsection{Purpose}

This document defines the user requirements for the new software project management
tool for the Demon Slayers Corps. This document will serve as a basis for both
stakeholders and developers in subsequent development activities.

\subsection{Project Background}

In a realm where demon slayers fought valiantly against the forces of darkness, the boss of
the Demon Slayer Corps struggled with managing their software projects, leading to chaotic
battles and the tragic loss of many brave warriors. Recognizing the dire need for better
organization, Kei, the CSCI3100 lecturer, and his eager students decided to step in, determined
to create a robust software project management tool tailored specifically for the Demon Slayers.

With their combined skills in coding and project management, they envisioned a system that
would streamline communication, track progress, and allocate resources effectively, ultimately
empowering the slayers to focus on their true mission: vanquishing demons and protecting
humanity.

\subsection{Business Objectives}
The high-level business objectives for the project are to:
\begin{enumerate}
    \item reduce inefficiency in task and resource allocation, including
    \begin{itemize}%[leftmargin=*]
        \item[(a)] average time from task creation to assignment;
        \item[(b)] workload variance across team members;
    \end{itemize}
    \item track mission and development progress in real time;
    \item streamline communication among developers;
    \item provide useful tools to facilitate software development;
\end{enumerate}

\subsection{Project Scope}
\subsubsection{Features}
The new project management tool aims to streamline software team coordination by 
providing task tracking, calendar scheduling, team discussion, and LLM chat interface to accelerate
development workflows.

The major functions to be provided by the tool are listed below:
\begin{enumerate}
    \item Kanban board for task management and progress tracking;
    \item Calendar to track and visualize deadlines;
    \item Discussion system to streamline communication among developers;
    \item LLM chat interface to speed up development progress;
\end{enumerate}

\subsubsection{Operating system}
Due to time constraint, the target platforms are limited to Apple's ecosystem, including
iOS, iPadOS and macOS. However, the technology must be easily extended to all platforms
in the future.