\section{Introduction}

\subsection{Purpose}

This document describes the architecture, system and user interface design for devban, a
software project management tool. This document will serve as a basis for developers
to implement the features in the application.

\subsection{Scope}

This document describes the design and implementation details of the devban
application. Due to time constraint, this document will limit the scope to Apple's platform only.

This document will focus on four components: 
database, users and teams management, UI design and the main features. 
Each of the components will be explained in details.

\subsection{Definitions, Acronyms and Abbreviations}
\begin{table}[h]
    \centering
    \caption{Definitions, Acronyms and Abbreviations}
    \begin{tabular}{p{2cm} p{12cm}}
        \toprule
        Acronyms
        & Description \\
        
        \midrule
        devban
        & Name of the project, shortened from ``develop'' and ``kanban'' \\

        \midrule
        UI
        & User Interface \\

        \midrule
        UX
        & User Experience \\

        \midrule
        GUI
        & Graphical User Interface \\

        \midrule
        MVVM
        & Model-View-ViewModel \\
 
        \bottomrule
    \end{tabular}
    \label{tab:docs_definitions_acronyms_and_abbreviations}
\end{table}

\subsection{References}
\begin{table}[h]
    \centering
    \caption{References}
    \begin{tabular}{p{1cm} p{3cm} p{8cm}}
        \toprule
        No.
        & Author
        & Reference \\
        
        \midrule
        Ref1
        & Ching-Yin Ng
        & QuestList \label{ref:QuestList}\\
 
        \bottomrule
    \end{tabular}
    \label{tab:references}
\end{table}

\subsection{Source Code}
The source code is available at \url{https://github.com/alvinng4/devban}.
To promote code quality, (1) all committed code must be formatted by swiftFormat,
(2) all linting warnings and errors by SwiftLint must be resolved. Furthermore,
the main branch is protected. Developers must create branches and create
pull request in order to merge into main.